---
title: "glmnet (averissimo fork)"
output: 
  github_document:
    toc: true
    dev: png
params:
  n.cores: !r 5
---

Fork of `glmnet` that implements mclapply instead of foreach in cross-validation with some speed-ups. 

The big improvement that can be seen in the tests below, is when adding `mclapply` in `cv.coxnet` for calculating deviances.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r, eval=FALSE, include=FALSE}
rmarkdown::render('README.Rmd')
```

## Required Libraries

```{r, message=FALSE, warning=FALSE}
library(microbenchmark)
library(devtools)
library(futile.logger)
library(testthat)
library(doMC)
library(ggfortify)
library(glmnet)
devtools::load_all()
```

## Load data from package itself

```{r}
data("CoxExample")
flog.info('x', head(x), capture = TRUE)
flog.info('y', head(y), capture = TRUE)
```

## Register doMC cores for classic glmnet package

```{r}
registerDoMC(cores=params$n.cores)
```

## Benchmark between glmnet and glmnet.mclapply

```{r}
microbenchmark::microbenchmark(
  glmnet.mclapply.no.parallel = glmnet.mclapply::cv.glmnet(x,y, family = 'cox'),
  glmnet.mclapply.with.parallel = glmnet.mclapply::cv.glmnet(x,y, family = 'cox', parallel = params$n.cores),
  glmnet.no.parallel = glmnet::cv.glmnet(x,y, family = 'cox'),
  glmnet.with.parallel = glmnet::cv.glmnet(x,y, family = 'cox', parallel=TRUE),
  times = 5)
```

## Testing if results are the same

*note*: There will be errors if this fails

```{r}
set.seed(1985)
res.mcl <- glmnet.mclapply::cv.glmnet(x,y, family = 'cox', parallel = params$n.cores)
set.seed(1985)
res.prl <- glmnet::cv.glmnet(x,y, family = 'cox', parallel=TRUE)

expect_equal(res.mcl$lambda.min, res.prl$lambda.min)
expect_equal(res.mcl$lambda.1se, res.prl$lambda.1se)
expect_equal(res.mcl$lambda, res.prl$lambda)

expect_equal(res.mcl$cvm, res.prl$cvm)
expect_equal(res.mcl$cvsd, res.prl$cvsd)
expect_equal(coef(res.mcl, 'lambda.min'), coef(res.prl, 'lambda.min'))

expect_equal(res.mcl$glmnet.fit$beta, res.prl$glmnet.fit$beta)

futile.logger::flog.info('Sucess!! results are the same')
```

## Plot the cross-validation

```{r, echo=FALSE}
loose.rock::multiplot(autoplot(res.mcl) + ggtitle('mclapply'),
                      autoplot(res.prl) + ggtitle('parallel'))
```


# Session Information

```{r session_info, echo=FALSE}
sessionInfo()
```

